Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-05-15 backscatter.tex
Fixed missing reference

If we focus on only one of the two generated images, or employ single
sideband backscatter~\cite{interscatter}, the data transmission can now
be received at frequency $f_d = f_c + \Delta f$.

>>>>

If we focus on only one of the two generated images, or employ single
sideband backscatter~\cite{iyer2016inter}, the data transmission can now
be received at frequency $f_d = f_c + \Delta f$.
